Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-10 sattose/paper.tex
Various changes

Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Approximately ten percent of the duplication can be refactored through method extraction without extra considerations required, while other clones require other refactoring techniques. Similar future measurements will provide further insight into the contexts where clones occur and how this affects the automated refactoring process. Finally, we strive to construct a tool that automatically applies refactorings for a large part of the detected duplication problems.
\end{abstract}

@@

Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in Table \ref{table:general}.

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \medskip
\begin{tabular}{|l|l|l|l|l|} \hline
\textbf{Relation}  & \textbf{\# (1)} & \textbf{\% (1)}  & \textbf{\# (1R)} & \textbf{\% (1R)} \\ \hline
Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

Another thread to validity is that currently, in a very small number of cases, clone detection might result in a false positive. This is in cases where two lines are equal, but they actually call different methods with the same method signature. In such a case, merging such clones might turn out to change the functionality of the program. Solving this problem is one of our next steps in this research.

>>>>

Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Approximately ten percent of the duplication can be refactored through method extraction without extra considerations required, while other clones require other refactoring techniques or further transformations. Similar future measurements will provide further insight into the contexts where clones occur and how this affects the automated refactoring process. Finally, we strive to construct a tool that automatically applies refactorings for a large part of the detected duplication problems.
\end{abstract}

@@

Some general data regarding this corpus is displayed in Table \ref{table:general}.

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \medskip
\begin{tabular}{|l|l|l|l|l|} \hline
\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
\end{tabular}
\end{center}
\end{table}

@@
